Neon: Nuclear Norm to Beat Muon

### 2025-05-06 poster/neon_poster.tex
added nanogpt validation loss (and train too but it does not fit on a poster, just uncomment in code if needed)
added description of Lanczos svd

\medskip
\hrule\medskip
\Head{Efficient update computation}\\
A couple of sentences about Lanczos algorithm and reference computation times and required number of iterations for tipical value of $\tau$.

@@

\medskip
\hrule\medskip
\Head{NanoGPT tests}\\
Couple of sentences and a vector(!) picture (reference picture for now).
\begin{figure}[h]
    \center{\includegraphics[width=0.8\linewidth]{../figs/mlp24/loss_val.png}}
    \caption{NanoGPT validation loss}
    \label{fig:nanogpt_loss}
\end{figure}

\medskip
\hrule\medskip
\Head{Conclusion}\\
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\medskip
\hrule\medskip
\Head{Efficient update computation}\\
% A couple of sentences about Lanczos algorithm and reference computation times and required number of iterations for tipical value of $\tau$.
We use cupy's svds routine to obtain gradients' matrices' SVD approximation formed by largest singular values and corresponding vectors.
By applying the Lanczos process to either $A^TA$ or $AA^T$, it generates a sequence of orthogonal vectors (Lanczos vectors) that capture 
the dominant spectral properties of the original matrix. The singular values and vectors are then extracted from the tridiagonal matrix using 
standard eigenvalue techniques like QR iteration.
\end{textblock}

@@

\medskip
\hrule\medskip
\Head{NanoGPT tests}\\
Couple of sentences and a vector(!) picture (reference picture for now).
% \begin{figure}[h]
%     \center{\includegraphics[width=0.8\linewidth]{../figs/mlp24/loss_val.png}}
%     \caption{NanoGPT validation loss}
%     \label{fig:nanogpt_loss}
% \end{figure} 
% \begin{figure}[h]
%     \center{\includegraphics[width=0.8\linewidth]{../figs/nanogpt/train_loss.pdf}}
%     \caption{NanoGPT train loss}
%     \label{fig:nanogpt_train_loss}
% \end{figure}
\begin{figure}[h]
    \center{\includegraphics[width=0.8\linewidth]{../figs/nanogpt/val_loss.pdf}}
    \caption{NanoGPT validation loss}
    \label{fig:nanogpt_val_loss}
\end{figure}
\medskip
\hrule\medskip
\Head{Conclusion}\\
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
